---
title: "Visualizing Star Wars characters"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r load-packages, include=FALSE}
library(tidyverse)
```

## Clone assignment repo

1. Go to your repo `appex02-[github_name]` on GitHub.

2. Click on the green **Clone or download** button, select **Use HTTPS** 
   (this might already be selected by default, and if it is, you'll see the 
   text **Clone with HTTPS** as in the image below). 
   Click on the clipboard icon to copy the repo URL.

3. Go to RStudio Cloud and into the STA 199 course workspace. 
   Create a **New Project from Git Repo**. You will need to click on the down 
   arrow next to the **New Project** button to see this option.

4. Copy and paste the URL of your assignment repo (done in step 2) into 
   the dialog box.

5. Click OK, and you should see the contents from your GitHub repo in the 
   `Files` pane in RStudio. 

## Configure git

Type the following lines of code in the **Console** in RStudio - filling in 
your name and email address.

```{r config-git-ex, eval=FALSE}
library(usethis)
use_git_config(user.name="your name", user.email="your email")
```

For example, mine would be  

```{r config-git-ex2, eval=FALSE}
library(usethis)
use_git_config(user.name="Shawn Santo", user.email="shawn.santo@duke.edu")
``````

**RStudio and GitHub can now communicate with each other and you are **
**ready to do the exercise below!**

## Some `ggplot2` practice

1. Modify the following plot to change the color of all points to a color of
   your choice. Adjust the figure width size and height as you see fit.

```{r starwars-plot, fig.width=8, fig.height=5}
ggplot(data = starwars, 
       mapping = aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(title = "_____" , size = "_____", x = "_____", y = "_____")
```

2. Add labels for `title`, `x` and `y` axes, and `size` of points. Knit again.

3. Try to create a histogram for the variable `mass` in `starwars`. Put your
   code in the chunk below.
   
```{r starwars-histogram}

```
   
## Stage, commit and push

1. Stage your modified Rmd file.
2. Commit your changes with message: "complete plots"
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.

**You will go over all of these steps again in tomorrow's lab**

## References

1. SWAPI - The Star Wars API . (2020). Swapi.co. 
   Retrieved from https://swapi.co/
