---
title: "Visualizing Starwars characters"
author: ""
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r load-packages, include=FALSE}
library(tidyverse)
```

## Clone assignment repo

1. Go to your `appex02-[username]` repo on GitHub.  
   Click on this repo.

2. Click on the green **Clone or download** button, select **Use HTTPS** 
   (this might already be selected by default, and if it is, you'll see the 
   text **Clone with HTTPS** as in the image below). 
   Click on the clipboard icon to copy the repo URL.

3. Go to RStudio Cloud and into the STA 199 course workspace. 
   Create a **New Project from Git Repo**. You will need to click on the down 
   arrow next to the **New Project** button to see this option.

4. Copy and paste the URL of your assignment repo into the dialog box.

5. Click OK, and you should see the contents from your GitHub repo in the 
   `Files` pane in RStudio. 

## Configure git

There is one more piece of housekeeping we need to take care of before we get 
started. Specifically,  we need to configure git so that RStudio can 
communicate with GitHub. This requires two pieces of information: 
your email address and your name.

Type the following lines of code in the **Console** in RStudio - filling in 
your name and email address.

```{r eval=FALSE}
library(usethis)
use_git_config(user.name="your name", user.email="your email")
```

For example, mine would be  

```{r eval=FALSE}
library(usethis)
use_git_config(user.name="Shawn Santo", user.email="shawn.santo@duke.edu")
``````

**RStudio and GitHub can now commmunicate with each other and you are **
**ready to do the exercise!**

## Some `ggplot2` practice

1. Modify the following plot to change the color of all points to `"pink"`. 
   Knit the document.

```{r starwars-plot}
ggplot(data = starwars, 
       mapping = aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(title = "_____" , size = "_____", x = "_____", y = "_____")
```

2. Add labels for title, x and y axes, and size of points. Knit again.

## Commit and push

1. Commit the changes you made using a simple and informative message. 
   You can find the Commit box in the Git tab in the top right pane.
2. Use the **green arrow** to push your changes to your repo on GitHub.
3. Enter your GitHub credentials when prompted.
4. Check your repo on GitHub and see the updated files.

**You will go over all of these steps again in tomorrow's lab, so it is OK if**
**you didn't get it all now!**
